\bf Hierarchical Network Structure Promotes Dynamical Robustness

### 2015-02-10 tex/methods.tex
add definition of total order to supplement

%!TEX root = ../paper.tex
\subsection{Monte carlo integration}\label{suppsec:montecarlo}
If we sample $N = N_{\mathrm{stab}} + N_{\mathrm{unstab}}$ matrices where each has some probability $\theta$ of being stable then $N_{\mathrm{stab}}$ has a binomial distribution. We can compute a sample estimate for $\theta$, $\hat{\theta} = \frac{N_{\mathrm{stab}}}{N}$ \cite{Murphy2012}. The posterior distribution in this case is known to be a Beta distribution as a result of Beta-Binomial conjugacy
$$
\mathrm{Beta}(\theta | \mathcal{D}) = \mathrm{Beta}(\theta | N_{\mathrm{stab}} + a, N_{\mathrm{unstab}} + b)
$$
where $a$ and $b$ are the hyperparameters of the Beta prior and we consider the uninformative uniform prior corresponding to $a=b=1$. We consider the maximum a posteriori estimate
$$\hat{\theta}_{MAP} = \frac{a + N_{\mathrm{stab}} - 1}{a + b + N - 2}$$
which corresponds in this case to the maximum likelihood estimate
$$
\hat{\theta}_{MLE} = \frac{N_{\mathrm{stab}}}{N}.
$$
This estimate is characterized by the variance of the posterior Beta distribution
% \begin{widetext}
\begin{align*}
&\mathrm{var}(\theta | \mathcal{D}) =\\
&\frac{(a+N_{\mathrm{stab}})(b+N_{\mathrm{unstab}})}{(a + N_{\mathrm{stab}} + b + N_{\mathrm{unstab}})^2(a + N_{\mathrm{stab}} + b + N_{\mathrm{unstab}}+1)}
\end{align*}
% \end{widetext}
Since for the chosen prior $a=b=1 \ll N$ this simplifies to
$$
\mathrm{var}(\theta | \mathcal{D}) = \frac{\hat{\theta}(1-\hat{\theta})}{N}
$$
yielding the error estimate given by the associated standard deviation. In all simulations we use $N~=~10000$ so that the maximum error for $\hat{\theta}~=~0.5$ is $\sigma~=~\sqrt{\mathrm{var}(\theta | \mathcal{D})} \approx 0.005$.

\subsection{Reaction Networks with Prescribed Connecctivity and Jacobians}\label{sec:reactionnetjacobian}

@@

>>>>

%!TEX root = ../paper.tex
\section{Reaction Networks with Prescribed Connecctivity and Jacobians}\label{sec:reactionnetjacobian}

@@

\section{Monte carlo integration}\label{suppsec:montecarlo}
If we sample $N = N_{\mathrm{stab}} + N_{\mathrm{unstab}}$ matrices where each has some probability $\theta$ of being stable then $N_{\mathrm{stab}}$ has a binomial distribution. We can compute a sample estimate for $\theta$, $\hat{\theta} = \frac{N_{\mathrm{stab}}}{N}$ \cite{Murphy2012}. The posterior distribution in this case is known to be a Beta distribution as a result of Beta-Binomial conjugacy
$$
\mathrm{Beta}(\theta | \mathcal{D}) = \mathrm{Beta}(\theta | N_{\mathrm{stab}} + a, N_{\mathrm{unstab}} + b)
$$
where $a$ and $b$ are the hyperparameters of the Beta prior and we consider the uninformative uniform prior corresponding to $a=b=1$. We consider the maximum a posteriori estimate
$$\hat{\theta}_{MAP} = \frac{a + N_{\mathrm{stab}} - 1}{a + b + N - 2}$$
which corresponds in this case to the maximum likelihood estimate
$$
\hat{\theta}_{MLE} = \frac{N_{\mathrm{stab}}}{N}.
$$
This estimate is characterized by the variance of the posterior Beta distribution
% \begin{widetext}
\begin{align*}
&\mathrm{var}(\theta | \mathcal{D}) =\\
&\frac{(a+N_{\mathrm{stab}})(b+N_{\mathrm{unstab}})}{(a + N_{\mathrm{stab}} + b + N_{\mathrm{unstab}})^2(a + N_{\mathrm{stab}} + b + N_{\mathrm{unstab}}+1)}
\end{align*}
% \end{widetext}
Since for the chosen prior $a=b=1 \ll N$ this simplifies to
$$
\mathrm{var}(\theta | \mathcal{D}) = \frac{\hat{\theta}(1-\hat{\theta})}{N}
$$
yielding the error estimate given by the associated standard deviation. In all simulations we use $N~=~10000$ so that the maximum error for $\hat{\theta}~=~0.5$ is $\sigma~=~\sqrt{\mathrm{var}(\theta | \mathcal{D})} \approx 0.005$.

\section{Hierarchy and Total ordering}\label{sec:totalordering}

A directed graph $G=(V,E)$ is a set $V$ of nodes and a set $E$ of ordered pairs of nodes \cite{Cormen2009}. For example, if $V = \{1,2,3\}$ and $E = \{(1,1),(2,2),(3,3),(1,2),(1,3),(2,3)\}$ then $G=(V,E)$ is the graph depicted in \reffigscc{} top where the labels $1$, $2$, and $3$ have been respectively assigned to the nodes vertically from top to bottom.

 We refer to the most hierarchical network architecture as the directed graph associated to a total ordering on the set of system components corresponding to the set of nodes, $V$, of the graph \cite{Cormen2009}. In general, a totally ordered set is a pair $(S,R)$ consisting of a set $S$ together with a total order relation $R$ on it. An example of a total ordering is the less than or equal to relation, $R \equiv \leq$, on the subset of natural numbers $S \equiv \{1,2,3\}$ given by $R \equiv \{1 \leq 1, 2 \leq 2, 3 \leq 3, 1 \leq 2, 1 \leq 3, 2 \leq 3\}$. The graph associated to this relation is equivalent to the graph shown in \reffigscc{} top and described algebraically in the preceding paragraph. More precisely, the conditions on $R$ for arbitrary elements $x,\,y,\,z \in S$ necessary for $(S,R)$ to be a totally ordered set are
\begin{enumerate}
\item If $x R y$ and $y R x$ then $x=y$ (antisymmetry)
\item If $x R y$ and $y R z$ then $x R z$ (transitivity)
\item $x R y$ or $y R x$ (totality)
\end{enumerate}
The totality condition implies $x R x$ (reflexivity) corresponding to the fact that the directed graph associated to the total ordering has, for each node, an edge whose source and target are the same node.
